---
title: "Benchmark"
author: "Leoni Zimmermann"
date: 28/08/2024
html:
  code-fold: true
  code-summary: "Show the code"
editor: visual
---

# Summary

This quarto document will go through the creation of the artifical dataset, MOFA and StabMap model and the calculation and visualization of different integration and imputation metrics.

# Data Preperation

## Libraries

```{r message=FALSE, warning=FALSE}
#---------------------------Seed------------------------------------------------
set.seed(42)
#---------------------------Libraries-------------------------------------------
library(MOFA2)
library(scater)
library(scran)
library(StabMap)
library(tidyverse)
library(cluster)
library(patchwork)
library(fpc)
library(MultiAssayExperiment)
library(plotly)

source("~/R/Functions/data_prep_functions.R")
source("~/R/Functions/integration_metrics_functions.R")
source("~/R/Functions/adaptiveKNN.R")
```

## Set values

```{r}
pathway_dataset <- "~/R/Data/data.RDS"

na_features <-  953:1740
na_cells <- 1:5016
```

## Preparing Data

Load Data

```{r}
# Peripheral Blood Mononuclear Cells provided by 10x Genomics website
# 10x Genomics Multiome technology enables simultaneous profiling of the transcriptome 
# (using 3’ gene expression) and epigenome (using ATAC-seq) from single cells to deepen 
# our understanding of how genes are expressed and regulated across different cell types.
# mae <- scMultiome("pbmc_10x", mode = "*", dry.run = FALSE, format = "MTX")

# Loaded from RDS cause I cant install the SingleCellMultiModal package
mae <- readRDS(pathway_dataset)
metadata <- mae@colData
```

Normalization

```{r}
# RNA
sce.rna <- normalize_and_select_features(experiments(mae)[["rna"]], 0.01, 0.05)

# ATAC
sce.atac <- normalize_and_select_features(experiments(mae)[["atac"]], 0.25, 0.05)

# Combine
logcounts_all_matrix <- as.matrix(rbind(logcounts(sce.rna), logcounts(sce.atac)))
```

## Some general dataframes etc.

```{r}
# Celltypes of all samples
all_celltypes <- as.data.frame(setNames(metadata$celltype, colnames(logcounts_all_matrix)))
colnames(all_celltypes) <- "celltype"

# Clusters
cluster <- as.data.frame(metadata) %>% 
  group_by(celltype) %>% 
  summarise(n = n()) %>% 
  mutate(n = 1:14) 
```

# Create input and training for MOFA and StabMap

## StabMap

```{r}
stab_list <- stab_build_model(data = logcounts_all_matrix, 
                              na_features =  na_features,
                              na_cells = na_cells)

mosaicDataUpSet(stab_list)
plot(mosaicDataTopology(stab_list))

# Training
stab = stabMap(stab_list,
               ncomponentsReference = 70,
               ncomponentsSubset = 70,
               reference_list = c("all_feat"),
               plot = FALSE,
               scale.center = FALSE,
               scale.scale = FALSE)

# UMAP
stab_umap_coord <- as.data.frame(calculateUMAP(t(stab)))


# Add metadata to the UMAP results (celltype, if it was an NA cell, cluster)
stab_umap <- merge( as.data.frame(metadata), stab_umap_coord, by =0 ) %>%
                mutate(isNA = if_else(Row.names %in% colnames(logcounts_all_matrix                                                        )[na_cells] , "NA", "notNA")) %>%  
                full_join(cluster) %>%
                column_to_rownames("Row.names")
```

## MOFA

```{r}
model <- mofa_build_model(data = logcounts_all_matrix, 
                          na_features = na_features,
                          na_cells = na_cells,
                          metadata = metadata)

plot_data_overview(model)

# Training
trained_model <- mofa_parameter_train(spikeslab_weights = FALSE, model = model)

# UMAP
trained_model <- run_umap(trained_model)
mofa_umap_coord <- trained_model@dim_red$UMAP %>% select(UMAP1, UMAP2)

# Add metadata to the UMAP results (celltype, if it was an NA cell, cluster)
mofa_umap <- merge(trained_model@dim_red$UMAP, all_celltypes, by = 0)  %>%
                full_join(cluster) %>% 
                mutate(isNA = if_else(sample %in% colnames(logcounts_all_matrix                                                        )[na_cells] , "NA", "notNA")) %>%  
                column_to_rownames("Row.names") %>%
                select(-sample)
```

# Integration

## Comparison UMAPS

```{r}
# MOFA
UM1 <- plot_dimred(trained_model, method = "UMAP", color_by = "celltype", dot_size =1) +           ggtitle("MOFA celltype")
UM2 <- plot_dimred(trained_model, method = "UMAP", color_by = "isNA", dot_size =1)+               ggtitle("MOFA NA")
UM3 <- plot_dimred(trained_model, method = "UMAP", color_by = "broad_celltype",dot_size =1)+ 
          ggtitle("MOFA broad celltype")

# StabMap
US1 <- ggplot(stab_umap) +
  geom_point(aes(x = UMAP1, y = UMAP2, color = celltype), size = .1) +
  theme_light() +
  ggtitle("StabMap celltype")
US2 <- ggplot(stab_umap) +
  geom_point(aes(x = UMAP1, y = UMAP2, color = isNA), size = .1) +
  theme_light() +
  ggtitle("StabMap NA")
US3 <- ggplot(stab_umap) +
  geom_point(aes(x = UMAP1, y = UMAP2, color = broad_celltype), size = .1) +
  theme_light() +
  ggtitle("StabMap broad celltype")

# Plot
combined_plot <- (UM1 + UM2 + UM3) / (US1 + US2 + US3) + plot_annotation(title = 'Comparison UMAP')
print(combined_plot)

# Interactive plots
# ggplotly(UM1)
```

There is no separation according to whether a cell has missing ATAC features or not. This means that the cells were not integrated based on this characteristic. When colouring by broad cell type (lymphoid or myeloid), a clear separation can be seen. f you analyse the plot for the specific cell type, a good separation can be seen where neighbouring clusters are mostly related cell types.

## Silhouette width

The silhouette width is a commonly used metric to assess clustering quality. It measures how similar an object (here: cell) is to its own cluster (here: celltype) compared to others. It ranges from 1 to -1 with higher values indicating better matches.

The mean silhouette width per cluster (in the following called silhouette score) is calculated for both "celltypes" and "cells with missing features" as cluster input.

```{r}
# StabMap celltype
stab_sil_sum <- silhouette_summary(stab_umap$n, stab_umap %>% select(UMAP1, UMAP2))
mean(stab_sil_sum$score)

# StabMap NA
stab_sil_sum_NA <- silhouette_summary(
  stab_umap %>% mutate(isNA = ifelse(isNA == "NA", 1, 0)) %>% pull(isNA),
  stab_umap %>% select(UMAP1, UMAP2))

# MOFA celltype
mofa_sil_sum <- silhouette_summary(mofa_umap$n, mofa_umap %>% select(UMAP1, UMAP2))
mean(mofa_sil_sum$score)

# MOFA NA 
mofa_sil_sum_NA <- silhouette_summary(
  mofa_umap %>% mutate(isNA = ifelse(isNA == "NA", 1, 0)) %>% pull(isNA), 
  mofa_umap %>% select(UMAP1, UMAP2))
```

"Cells with missing features" cluster:

For both StabMap and MOFA the results for the score are close to zero, suggesting a well mixture.

"Celltypes" clusters:

Cluster five (effector CD8 T cells) has a negative score, suggesting bad clustering. The number of clusters with a score below 0.5 (considered as reasonable) is seven for MOFA and 9 for StabMap out of 14 clusters total.

The mean scores are 0.46 for MOFA and 0.42 for StabMap.

## More cluster stats

More cluster stats that could be of interest:

```{r}
stab_cluster_stats <- cluster.stats(dist(stab_umap %>% select(UMAP1, UMAP2)), stab_umap$n)
mofa_cluster_stats <- cluster.stats(dist(mofa_umap %>% select(UMAP1, UMAP2)), mofa_umap$n)
```

## Celltype accuracy

This metric was taken from the StabMap paper. Their description:

Given a joint embedding, we perform a simulation such that discrete class labels corresponding to cell types are artificially removed for a subset of the data. We then perform k-nearest neighbors classification (k=5) to obtain the predicted class label for the artificially unlabeled data. The cell type classification accuracy is thus the proportion of cells for which the classification is correct compared to the true cell type label

The cell labels from atac_query are the removed ones.

uniformed_fixed denotes that there is one fixed k for all cells.

While knn_acc is the accuracy of the k-NN predictions, knn_acc_bal represents the balanced accuracy, giving equal weight to each cell type regardless of its size. knn_acc_bal will be used for later evaluation since some clusters have more cells than others.

```{r}
# Predict "RNA only" cell's cell types 
# Split Data
rna_train <- stab_umap$celltype[na_cells]
names(rna_train) <- rownames(stab_umap)[na_cells]
atac_query <- stab_umap$celltype[setdiff(1:ncol(logcounts_all_matrix), na_cells)]
names(atac_query) <- rownames(stab_umap)[setdiff(1:ncol(logcounts_all_matrix), na_cells)]

# StabMap
stab_knn_out = embeddingKNN(stab_umap_coord,
                       rna_train,
                       type = "uniform_fixed",
                       k_values = 5)
stab_knn_acc = mean(isEqual(stab_knn_out[names(atac_query),"predicted_labels"], atac_query), na.rm = TRUE)
stab_knn_acc_bal = mean(unlist(lapply(split(isEqual(stab_knn_out[names(atac_query),"predicted_labels"], atac_query), atac_query), mean, na.rm = TRUE)))

# MOFA
mofa_knn_out = embeddingKNN(mofa_umap_coord,
                       rna_train,
                       type = "uniform_fixed",
                       k_values = 5)
mofa_knn_acc = mean(isEqual(mofa_knn_out[names(atac_query),"predicted_labels"], atac_query), na.rm = TRUE)
mofa_knn_acc_bal = mean(unlist(lapply(split(isEqual(mofa_knn_out[names(atac_query),"predicted_labels"], atac_query), atac_query), mean, na.rm = TRUE)))

# Result
cat(" Accuracy StabMap: ", stab_knn_acc,"/",stab_knn_acc_bal,"(per celltype)", "\n","Accuracy MOFA: ", mofa_knn_acc,"/",mofa_knn_acc_bal,"(per celltype)")
```

The MOFA method demonstrates superior cell type accuracy in comparison to StabMap, which is likely attributed to the more effective clustering by MOFA.

# Imputation

```{r}
# StabMap
imp = imputeEmbedding(
  stab_list,
  stab,
  reference = colnames(stab_list[["all_feat"]]),
  query = colnames(stab_list[["missing_feat"]]))

# MOFA
trained_model <- impute(trained_model)
```

## RMSE

The root mean square error measures the difference between predicted and observed values. This is possible since the dataset has artifically removed ATAC features for half of the cells.

```{r}
# StabMap
stab_rmse <- rmse_imp(imp_data = imp$all_feat[na_features,], 
                      real_data = logcounts_all_matrix, 
                      na_features = na_features, 
                      na_cells = na_cells)

# MOFA
mofa_rmse<- rmse_imp(imp_data = trained_model@imputed_data$missing_feat[[1]][,na_cells],
                     real_data = logcounts_all_matrix, 
                     na_features = na_features, 
                     na_cells = na_cells)

cat(" StabMap RMSE:", stab_rmse, "\n", "MOFA RMSE:",mofa_rmse )
```

MOFA shows a smaller and thus better RMSE than StabMap.
